Democratizing Secure Two-Party Computation

### 2017-10-17 OaklandSubmission/intro.tex
intro contrib

@@

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation that achieves generality, performance and programmer
productivity. The programmer writes a high level \divya{C-like}
program (instead of a circuit) to describe the function to be
computed. Our compiler automatically generates an \mpc protocol using a
mix of Arithmetic and Boolean compute. Our compiler is general and can
work with any secure implementation of a mix of arithmetic and boolean
computations. In our work, we focus on semi-honest secure two-party
computation. We build on ABY \cite{aby} that provides the suitable
cryptographic back-end in this setting. We provide a formal type
system and prove correctness and security of our compiler. We evaluate
our system on various benchmarks such as logistic regression and
convolutional neural network (CNN) for MNIST data \cite{minionn},
naive bayes, decision trees from \cite{shafindss}. Evaluations show
that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). Below, we will  give an overview of \tool and
describe our contributions in more detail.

@@

>>>>

  \divya{Do we write the intro for \mpc or 2PC?}

@@

%\divya{old para...} In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
%computation that achieves generality, performance and programmer
%productivity. The programmer writes a high level \divya{C-like}
%program (instead of a circuit) to describe the function to be
%computed. Our compiler automatically generates an \mpc protocol using a
%mix of Arithmetic and Boolean compute. Our compiler is general and can
%work with any secure implementation of a mix of arithmetic and boolean
%computations. In our work, we focus on semi-honest secure two-party
%computation. We build on ABY \cite{aby} that provides the suitable
%cryptographic back-end in this setting. We provide a formal type
%system and prove correctness and security of our compiler. We evaluate
%our system on various benchmarks such as logistic regression and
%convolutional neural network (CNN) for MNIST data \cite{minionn},
%naive bayes, decision trees from \cite{shafindss}. Evaluations show
%that protocols generated by our compiler match
%the performance or outperform hand-crafted protocols in most cases (see
%\sectionref{eval}). Below, we will  give an overview of \tool and
%describe our contributions in more detail.

@@

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of Arithmetic and Boolean compute. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean computations. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks \cite{shafindss,wu,minionn,valeriaMatrix} computing linear classifier, decision trees, deep neural networks, and matrix factorization. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \divya{Moreover, unlike previous systems, our system can scale to arbitrarily large computations using {\em pipelining} (see below). What do we say about Yao pipelining?}
Hence, we show that our framework achieves all three properties of generality, performance and programmer productivity.

\divya{Points.. 1. Prior to our work, there was CBMGC no perf; ABY no prog; 
3. Programmability allows writing programs generating large circuits... 
}

Below, we describe the salient features of \tool in more detail.
